### 2015-06-04 LOI/inc2.tex
reordered the software stack and proposed work paragraphs

\underline{\textbf{Objectives:}} Exascale scientific discovery will
%introduce more complex hardware, and many simulations will 
be bottlenecked 
without sufficient new research into managing and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to investigate a unique approach to addressing this challenge in
a multi-tier storage platform, expediting insights into mission critical
scientific processes. 
% the multi-tier challenges that are faced by scientists in creating and
% managing and storing their data  to expedite insights xsinto
% mission critical scientific processes in exascale compuxsting.
%
We propose a research program that aims to explore a hiearchical
organization and storage infstraturure which will facilitiate how data can
be written to and read from a complex heterogenous storage hierarchy
efficiently. In order to explore the many research challenges in this
domain, we will build upon the success of our middleware system, ADIOS, our
multi-tier storage system, Sirocco, and our distributed storage system,
Ceph.  We will also leverage data movement and staging technologies, Data
Spaces and the Common Communication Interface (CCI), as part of a software
stack used successfully on current leadership class machines. Our experience
with this stack will guide us in understanding the new directions for
research in storage systems and I/O for exascale and beyond systems.

@@

%
We will apply a technique which will re-organize and possibly reduce the total amount of information based on user intentions along
with direct feedback from the storage and I/O system to allow data to be optimized not just for output, but also for many of the complex
reading patterns. Since data analysis and visualization will be performed in both an in situ and post processing environment, 
we will continue to use our I/O and storage abstractions to help enable applications to take full advantage of the hardware and softare 
environments. Because data volumes are strictly outstripping available bandwidths, compression will
be required. Rather than focusing solely on lossless compression, we will
incorporate lossy compression with the ability to annotate data allowing
optimized algorithm selection based on the numerical methods employed in the
source simulation. We plan to epxlore this tradeoff of storage capacity and
bandwidth for computation to determine how to offer the user options that can
meet their needs with desireable performance characteristics.
%
Our objective is to reduce the time to knowledge, which means that we will also support additional access modes, beyond the traditional 
Checkpoint/Restart methods, and understand that all data has errors associated with it and we will ensure that these become encoded to allow
for additional optimizations. For example, all scientific simulations contain approximations, and all measurements from obervations and experiments 
also contain errors. These errors can help guide how information can be presented to users, by allowing us to ask for information within a given 
accuracy bound, and also allow us to offer a mode for recomputation vs. data storage and reterival.  
%
{\bf: please list other things from UCSC, OLCF}.
%

>>>>

\underline{\textbf{Objectives:}} Exascale scientific discovery will
%introduce more complex hardware, and many simulations will 
be bottlenecked 
without sufficient new research into managing and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to investigate a unique approach to addressing this challenge in
a multi-tier storage platform, expediting insights into mission critical
scientific processes. 
% the multi-tier challenges that are faced by scientists in creating and
% managing and storing their data  to expedite insights xsinto
% mission critical scientific processes in exascale compuxsting.
%
We propose a research program that aims to explore a hiearchical
organization and storage infstraturure which will facilitiate how data can
be written to and read from a complex heterogenous storage hierarchy
efficiently.  
%
We will apply a technique which will re-organize and possibly
reduce the total amount of information based on user intentions along with
direct feedback from the storage and I/O system to allow data to be
optimized not just for output, but also for many of the complex reading
patterns. Since data analysis and visualization will be performed in both an
in situ and post processing environment, we will continue to use our I/O and
storage abstractions to help enable applications to take full advantage of
the hardware and softare environments. Because data volumes are strictly
outstripping available bandwidths, compression will be required. Rather than
focusing solely on lossless compression, we will incorporate lossy
compression with the ability to annotate data allowing optimized algorithm
selection based on the numerical methods employed in the source
simulation. We plan to epxlore this tradeoff of storage capacity and
bandwidth for computation to determine how to offer the user options that
can meet their needs with desireable performance characteristics.

In order to explore the many research challenges in this
domain, we will build upon the success of our middleware system, ADIOS, our
multi-tier storage system, Sirocco, and our distributed storage system,
Ceph.  We will also leverage data movement and staging technologies, Data
Spaces and the Common Communication Interface (CCI), as part of a software
stack used successfully on current leadership class machines. Our experience
with this stack will guide us in understanding the new directions for
research in storage systems and I/O for exascale and beyond systems.

@@

%

%
Our objective here is to reduce the time to knowledge, an end-to-end metric
relevant to the scientific discovery process. Beyond the traditional high
volume I/O pattern of checkpoint/restart, we will address the challenges
posed by additional data access patterns in the knowledge gathering
process. With a deeper insight into the scientific process we will encode
and utilize errors and accuracy as an optimization parameter. For example, 
%
% We will explore access to
% large data sets as part of this process, w

% which means that we will
% also support additional access modes, beyond the traditional
% Checkpoint/Restart methods, and understand that all data has errors
% associated with it and we will ensure that these become encoded to allow for
% additional optimizations. 
For example, all scientific simulations contain
approximations, and all measurements from obervations and experiments also
contain errors. These errors can help guide how information can be presented
to users, by allowing us to ask for information within a given accuracy
bound, and also allow us to offer a mode for recomputation vs. data storage
and reterival.

%
{\bf: please list other things from UCSC, OLCF}.
%
